### 2022-04-01 manuscript.tex
r [ci skip]
This build is based on
https://github.com/scherzerthesis/thesis/commit/fcabaebc95d4706a4292867fd20157e9518a14a5.

This commit was created by the following CI build and job:
https://github.com/scherzerthesis/thesis/commit/fcabaebc95d4706a4292867fd20157e9518a14a5/checks
https://github.com/scherzerthesis/thesis/actions/runs/2074393277

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/92ef2d831287c2ff7b407a0430e34b450ef9997c/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/92ef2d831287c2ff7b407a0430e34b450ef9997c}{scherzerthesis/thesis@92ef2d8}
on March 31, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgf1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgf2.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

>>>>

This manuscript
(\href{https://scherzerthesis.github.io/thesis/v/fcabaebc95d4706a4292867fd20157e9518a14a5/}{permalink})
was automatically generated
from \href{https://github.com/scherzerthesis/thesis/tree/fcabaebc95d4706a4292867fd20157e9518a14a5}{scherzerthesis/thesis@fcabaeb}
on April 1, 2022.

@@

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr1.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}

\begin{figure}
\hypertarget{fig:04}{%
\centering
\includegraphics[width=1\textwidth,height=\textheight]{images/pdgfr2.png}
\caption{\textbf{This is the title of Figure} this is the text.**}\label{fig:04}
}
\end{figure}
